---
title: "Dr. Waldrop's Notebook"
output: html_notebook
---

# Some initial plotting

## 25-hair array

Loading data and shaping data frame:
```{r echo=TRUE, message=TRUE, warning=TRUE}
library(ggplot2) # for ggplots
library(reshape2) # for melt()
library(viridis) # for the viridis color palette
# parameter values
parameters<-read.csv("../data/parameters/allpara_165.txt", header=FALSE, sep = "\t")
names(parameters)<-c("angle","gap","Re")
# 25-hair array
nohairs<-25
waterdata.25 <- read.csv("../results/r-csv-files/25hair_results/totalconc_165_2020-11-29.csv")
waterdata.25 <- data.frame(parameters,waterdata.25)
waterhairs25<-data.frame(parameters,waterdata.25[,2:(1+nohairs)])
waterhairs25.melted<-melt(waterhairs25,id.vars = c("angle","gap","Re"))
# 18-hair array
nohairs<-18
alldata.18 <- read.csv("../results/r-csv-files/18hair_results/totalconc_165_2020-11-29.csv")
hairs18<-data.frame(parameters,alldata.18[,2:(1+nohairs)])
hairs18.melted<-melt(hairs18,id.vars = c("angle","gap","Re"))
```

## Hair plots

### 25-hair array

Plot Reynolds number versus odor concentration captured:
```{r echo=FALSE}
ggplot(hairs25.melted, aes(Re,value,color=variable))+geom_point()+scale_color_viridis(discrete=TRUE)
```

Plot gap-to-diameter ratio against value: 
```{r echo=FALSE}
ggplot(hairs25.melted, aes(gap,value,color=variable))+geom_point()+scale_color_viridis(discrete=TRUE)
```


Plot angle versus value:
```{r echo=FALSE}
ggplot(hairs25.melted, aes(angle,value,color=variable))+geom_point()+scale_color_viridis(discrete=TRUE)
```

## Total Concentration Plots

Total concentration for gap-to-diameter ratio versus odor captured as color: 
```{r echo=FALSE}
ggplot(alldata.25, aes(gap,total.conc,color=total.conc))+geom_point()+scale_color_viridis()
```

Total concentration for Re versus odor captured as color: 
```{r echo=FALSE}
ggplot(alldata.25, aes(Re,total.conc,color=total.conc))+geom_point()+scale_color_viridis()
```

Total concentration for gap-to-diameter ratio versus odor captured as color: 
```{r echo=FALSE}
ggplot(alldata.25, aes(angle,total.conc,color=total.conc))+geom_point()+scale_color_viridis()
```


## 18-hair array


### Hair plots

Plot Reynolds number versus odor concentration captured:
```{r echo=FALSE}
ggplot(hairs18.melted, aes(Re,value,color=variable))+geom_point()+scale_color_viridis(discrete=TRUE)
```
