---
title: "Dr. Waldrop's Odor-capture Notebook"
output:
  html_notebook: default
  pdf_document: default
  html_document:
    df_print: paged
fig_width: 8.5
---

# Some initial plotting for the water condition

Loading data and shaping data frame:
```{r echo=TRUE, message=TRUE, warning=FALSE}
library(ggplot2) # for ggplots
library(cowplot) # for plot_grid()
library(reshape2) # for melt()
library(viridis) # for the viridis color palette

# Sourcing data handling functions
source("../src/r-scripts/datahandling_functions.R")

n <- 165 # Number of simulations in set

# Loading individual data sets
waterdata_3 <- loadnshapedata(n,"totalconc_water",3,"2020-12-08")
waterdata_5 <- loadnshapedata(n,"totalconc_water",5,"2020-12-25")
waterdata_7 <- loadnshapedata(n,"totalconc_water",7,"2020-12-21")
waterdata_12 <- loadnshapedata(n,"totalconc_water",12,"2020-12-19")
waterdata_18 <- loadnshapedata(n,"totalconc_water",18,"2020-12-04")
waterdata_25 <- loadnshapedata(n,"totalconc_water",25,"2020-12-04")
airdata_3 <- loadnshapedata(n,"totalconc_air",3,"2020-12-08")
airdata_5 <- loadnshapedata(n,"totalconc_air",5,"2020-12-26")
airdata_7 <- loadnshapedata(n,"totalconc_air",7,"2020-12-21")
airdata_12 <- loadnshapedata(n,"totalconc_air",12,"2020-12-19")
airdata_18 <- loadnshapedata(n,"totalconc_air",18,"2020-12-04")
airdata_25 <- loadnshapedata(n,"totalconc_air",25,"2020-12-04")

water.data <- list("3" = waterdata_3, "5" = waterdata_5,
                   "7" = waterdata_7, "12" = waterdata_12, 
                   "18" = waterdata_18, "25" = waterdata_25)
air.data <- list("3" = airdata_3, "5" = airdata_5,
                 "7" = airdata_7, "12" = airdata_12,
                 "18" = airdata_18, "25" = airdata_25)
list.hairs <- c("3","5","7","12","18","25")
alldatarow.water<-stitch.rows(water.data,list.hairs)
alldatarow.air<-stitch.rows(air.data,list.hairs)



# Loads plotting data
data.3hair <- plot.hairs(3)
data.5hair <- plot.hairs(5) 
data.7hair <- plot.hairs(7) 
data.12hair <- plot.hairs(12) 
data.18hair <- plot.hairs(18) 
data.25hair <- plot.hairs(25)
```

## Methods

We created six hair arrays with different numbers of hairs and configurations. The number of hairs varied (3, 5, 7, 12, 18, and 25 hairs) in one to five rows of hairs (3 and 5 hairs in 1 row, 7 hairs in two rows, 12 hairs in 3 rows, 18 hairs in 4 rows, and 25 hairs in 5 rows). 

```{r, echo=FALSE}
plot.3hair <- ggplot(data.3hair, aes(x, y, color=antorhair)) + geom_point(size = 0.5) + 
  xlim(-0.05,0.25) + ylim(-0.17, 0.17) + scale_color_manual(values=c("gray60","black"), name =" ") +
  theme_bw() + theme(plot.margin = unit(c(0.75,0.57,0,0),"cm"), legend.position = "none")
plot.5hair <- ggplot(data.5hair, aes(x, y, color=antorhair)) + geom_point(size = 0.5) + 
  xlim(-0.05,0.25) + ylim(-0.17, 0.17) + scale_color_manual(values=c("gray60","black"), name =" ") +
  theme_bw() + theme(plot.margin = unit(c(0.75,0.57,0,0),"cm"), legend.position = "none")
plot.7hair <- ggplot(data.7hair, aes(x, y, color=antorhair)) + geom_point(size = 0.5) + 
  xlim(-0.05,0.25) + ylim(-0.17, 0.17) + scale_color_manual(values=c("gray60","black"), name =" ") +
  theme_bw() + theme(plot.margin = unit(c(0.75,0.57,0,0),"cm"), legend.position = "none")
plot.12hair <- ggplot(data.12hair, aes(x, y, color=antorhair)) + geom_point(size = 0.5) + 
  xlim(-0.05,0.25) + ylim(-0.17, 0.17) + scale_color_manual(values=c("gray60","black"), name =" ") +
  theme_bw() + theme(plot.margin = unit(c(0.75,0.57,0,0),"cm"), legend.position = "none")
plot.18hair <- ggplot(data.18hair, aes(x, y, color=antorhair)) + geom_point(size = 0.5) + 
  xlim(-0.05,0.25) + ylim(-0.17, 0.17) + scale_color_manual(values=c("gray60","black"), name =" ") +
  theme_bw() + theme(plot.margin = unit(c(0.75,0.57,0,0),"cm"), legend.position = "none")
plot.25hair <- ggplot(data.25hair, aes(x, y, color=antorhair)) + geom_point(size = 0.5) + 
  xlim(-0.05,0.25) + ylim(-0.17, 0.17) + scale_color_manual(values=c("gray60","black"), name =" ") +
  theme_bw() + theme(plot.margin = unit(c(0.75,0.57,0,0),"cm"), legend.position = "none")
#2 rows, 3 columns
#png(file="hair-configs.png",height=6,width=8.5,unit="in",res=600)
#plot_grid(plot.3hair, plot.5hair, plot.7hair, plot.12hair, plot.18hair, plot.25hair, 
#          labels = c("3 hairs, 1 row", "5 hairs, 1 row", "7 hairs, 2 rows", 
#                     "12 hairs, 3 rows", "18 hairs, 4 rows", "25 hairs, 5 rows"))
#dev.off()
#3 rows, 2 columns
#png(file="hair-configs.png",height=8.5,width=6,unit="in",res=600)
plot_grid(plot.3hair, plot.5hair, plot.7hair, plot.12hair, plot.18hair, plot.25hair, 
          nrow = 3,
          labels = c("3 hairs, 1 row", "5 hairs, 1 row", "7 hairs, 2 rows", 
                     "12 hairs, 3 rows", "18 hairs, 4 rows", "25 hairs, 5 rows"))
#dev.off()

```

## Preliminary Results

### 1. It's better to have more hairs in water and fewer hairs in air.

We can set up data frames that will compare for us in separate plots the total odor concentration caught by each array in air or water.
```{r echo=TRUE}
alldatawater.totalconc <- data.frame(waterdata_3[,1:3], 
                                     waterdata_3$total.conc, 
                                     waterdata_5$total.conc,
                                     waterdata_7$total.conc, 
                                     waterdata_12$total.conc, 
                                     waterdata_18$total.conc, 
                                     waterdata_25$total.conc)
colnames(alldatawater.totalconc)<- c(colnames(waterdata_3[,1:3]),
                                 "3hairs","5hairs","7hairs", 
                                 "12hairs","18hairs","25hairs")
alldatawaterconc.melted <- melt(alldatawater.totalconc, 
                                id.vars = c("angle","gap","Re"))
alldataair.totalconc <- data.frame(airdata_3[,1:3], airdata_3$total.conc,
                                   airdata_5$total.conc, airdata_7$total.conc,
                                   airdata_12$total.conc, airdata_18$total.conc,
                                   airdata_25$total.conc)
colnames(alldataair.totalconc)<- c(colnames(airdata_3[,1:3]),
                                  "3hairs","5hairs","7hairs", 
                                  "12hairs","18hairs","25hairs")
alldataairconc.melted <- melt(alldataair.totalconc, 
                              id.vars = c("angle","gap","Re"))
```

From here, we can plot the mean total concentration captured by each array for water and air: 

```{r echo = FALSE, warning = FALSE}
labelair.df <- data.frame(variable=c("3hairs","5hairs","7hairs","12hairs","18hairs","25hairs"), value=c(30000,NA,NA,NA,NA,NA))
labelwater.df <- data.frame(variable=c("3hairs","5hairs","7hairs","12hairs","18hairs","25hairs"), value=c(200,NA,NA,NA,NA,NA))

all.water <- ggplot(alldatawaterconc.melted, aes(variable, value, fill = variable)) + 
  geom_violin(color = "gray30") +
  stat_summary(fun = "mean", color = "gray30", fill = "white", pch = 21, 
               size = 1.25) +
  scale_fill_viridis(name = "Array", discrete = TRUE) + 
  geom_point(data=labelwater.df, 
             mapping=aes(x=variable,y=value),color="black",pch="*",size=6) +
  xlab("") + ylab("Total Conc Captured") + ggtitle("Water") +
  theme_bw() + theme(plot.title = element_text(hjust = 0.5), legend.position = "none")

all.air <- ggplot(alldataairconc.melted, aes(variable, value, fill = variable)) +
  geom_violin(color = "gray30") +
  stat_summary(fun = "mean", color = "black", fill = "white", pch = 21, 
               size = 1.25)+
  scale_fill_viridis(name = "Array", discrete = TRUE, option = "C") + 
  geom_point(data=labelair.df, 
             mapping=aes(x=variable,y=value),color="black",pch="*",size=6) +
  xlab("") + ylab("Total Conc Captured") + ggtitle("Air") + 
  theme_bw() + theme(plot.title = element_text(hjust = 0.5), legend.position = "none")
#png(file = "total.conc.violin.png", height = 2.5, width = 5.6, unit = "in", res = 500)
plot_grid(all.water, all.air, labels = c("Water","Air"), 
          label_x = c(0.5, 0.5), label_y = c(1.1, 1.1))
#dev.off()
```


```{r,warning=FALSE,echo=FALSE,error=FALSE}
model.water312<-t.test(alldatawater.totalconc[,4],alldatawater.totalconc[,5])
model.water318<-t.test(alldatawater.totalconc[,4],alldatawater.totalconc[,6])
model.water325<-t.test(alldatawater.totalconc[,4],alldatawater.totalconc[,7])
model.water1218<-t.test(alldatawater.totalconc[,5],alldatawater.totalconc[,6])
model.water1225<-t.test(alldatawater.totalconc[,5],alldatawater.totalconc[,7])
model.water1825<-t.test(alldatawater.totalconc[,6],alldatawater.totalconc[,7])


model.air312<-t.test(alldataair.totalconc[,4],alldataair.totalconc[,5])
model.air318<-t.test(alldataair.totalconc[,4],alldataair.totalconc[,6])
model.air325<-t.test(alldataair.totalconc[,4],alldataair.totalconc[,7])
model.air1218<-t.test(alldataair.totalconc[,5],alldataair.totalconc[,6])
model.air1225<-t.test(alldataair.totalconc[,5],alldataair.totalconc[,7])
model.air1825<-t.test(alldataair.totalconc[,6],alldataair.totalconc[,7])
```

Here we can see that in water, it's slightly better to have more hairs, and in some cases, a lot better. The 3-hair array captures significantly less odor than the 12-hair array ($t = `r signif(model.water312$statistic,digits=3)`$, $p = `r signif(model.water312$p.value,digits=1)`$), the 18-hair array ($t = `r signif(model.water318$statistic,digits=3)`$, $p = `r signif(model.water318$p.value,digits=1)`$), and the 25-hair array ($t = `r signif(model.water325$statistic,digits=3)`$, $p = `r signif(model.water325$p.value, digits=1)`$). The odor captured by the 18-hair and 25-hair arrays was not different from each other ($t = `r signif(model.water1825$statistic,digits=3)`$, $p = `r signif(model.water1825$p.value,digits=1)`$).

However, in air it's generally better to have fewer hairs. Even though there is less surface area available to capture odor, totals were on average higher for the 3-hair array than for 12-hair ($t = `r signif(model.air312$statistic,digits=3)`$, $p = `r signif(model.air312$p.value,digits=1)`$), 18-hair ($t = `r signif(model.air318$statistic,digits=3)`$, $p = `r signif(model.air318$p.value,digits=1)`$), or 25-hair ($t = `r signif(model.air325$statistic,digits=3)`$, $p = `r signif(model.air325$p.value,digits=1)`$) arrays. Once again, odor captured by the 18-hair and 25-hair arrays were not different from each other ($t = `r signif(model.air1825$statistic,digits=3)`$, $p = `r signif(model.air1825$p.value,digits=1)`$). 

We can also plot the total concentration captured against each of the three parameters for air and water: 
```{r echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, fig.height = 10, fig.width = 8.5}
#fig.height=4.5, fig.width=4.25}
water.gap <- ggplot(alldatawaterconc.melted, aes(gap, value, fill = variable)) +
            geom_point(size = 4, pch = 21, color = "gray30") +           
            geom_smooth(aes(fill=variable,color=variable)) +
            scale_fill_viridis(name = "Array", discrete = TRUE) +
            scale_color_viridis(name = "Array", discrete = TRUE) +
            xlab("Gap-to-diameter ratio") + ylab("Total odor captured") +
            theme_bw() + theme(legend.position = "left")
leg.water<-get_legend(water.gap)
water.gap <- ggplot(alldatawaterconc.melted, aes(gap, value, fill = variable)) +
            geom_point(size = 2.5, pch = 21, color = "gray30") + 
            geom_smooth(aes(fill=variable,color=variable)) +
            scale_fill_viridis(name = "Array", discrete = TRUE) +
            scale_color_viridis(name = "Array", discrete = TRUE) +
            xlab("Gap-to-diameter ratio") + ylab("Total odor captured") +
            theme_bw() + theme(legend.position = "none")
air.gap <- ggplot(alldataairconc.melted, aes(gap, value, fill = variable)) +
            geom_point(size = 4, pch = 21, color = "gray30") + 
            geom_smooth(aes(fill=variable,color=variable)) +
            scale_fill_viridis(name = "Array", discrete = TRUE, option = "C") +
            scale_color_viridis(name = "Array", discrete = TRUE, option = "C") +
            xlab("Gap-to-diameter ratio") + ylab("Total odor captured") + 
            theme_bw() + theme(legend.position = "left")
leg.air<-get_legend(air.gap)
air.gap <- ggplot(alldataairconc.melted, aes(gap, value, fill = variable)) +
            geom_point(size = 2.5, pch = 21, color = "gray30") + 
            geom_smooth(aes(fill=variable,color=variable)) +
            scale_fill_viridis(name = "Array", discrete = TRUE, option = "C") +
            scale_color_viridis(name = "Array", discrete = TRUE, option = "C") +
            xlab("Gap-to-diameter ratio") + ylab("Total odor captured") + 
            theme_bw() + theme(legend.position = "none")
water.Re <- ggplot(alldatawaterconc.melted, aes(Re, value, fill = variable)) +
            geom_point(size = 2.5, pch = 21, color = "gray30") + 
            geom_smooth(aes(fill=variable,color=variable)) +
            scale_fill_viridis(name = "Array", discrete = TRUE) +
            scale_color_viridis(name = "Array", discrete = TRUE) +
            xlab("Reynolds number") + ylab("Total odor captured") +
            theme_bw() + theme(legend.position = "none")
air.Re <- ggplot(alldataairconc.melted, aes(Re, value, fill = variable)) +
            geom_point(size = 2.5, pch = 21, color = "gray30") + 
            geom_smooth(aes(fill=variable,color=variable)) +
            scale_fill_viridis(name = "Array", discrete = TRUE, option = "C") +
            scale_color_viridis(name = "Array", discrete = TRUE, option = "C") +
            xlab("Reynolds number") + ylab("Total odor captured") + 
            theme_bw() + theme(legend.position = "none")
water.angle <- ggplot(alldatawaterconc.melted, aes(angle, value, fill = variable)) +
            geom_point(size = 2.5, pch = 21, color = "gray30") + 
            geom_smooth(aes(fill=variable,color=variable)) +
            scale_fill_viridis(name = "Array", discrete = TRUE) +
            scale_color_viridis(name = "Array", discrete = TRUE) +
            xlab("Angle") + ylab("Total odor captured") +
            theme_bw() + theme(legend.position = "none")
air.angle <- ggplot(alldataairconc.melted, aes(angle, value, fill = variable)) +
            geom_point(size = 2.5, pch = 21, color = "gray30") + 
            geom_smooth(aes(fill=variable,color=variable)) +
            scale_fill_viridis(name = "Array", discrete = TRUE, option = "C") +
            scale_color_viridis(name = "Array", discrete = TRUE, option = "C") +
            xlab("Angle") + ylab("Total odor captured") + 
            theme_bw() + theme(legend.position = "none")

#png(filename = "three-parameters.png", height = 10, width = 8.5, unit="in",res=600)
plot_grid(leg.water, leg.air, water.gap, air.gap, water.Re, air.Re, water.angle, air.angle,
          nrow = 4,
          labels=c("Water", "Air"), 
          label_x = c(0.45,0.45), 
          label_y = c(1, 1),
          rel_heights = c(0.75,2,2,2),rel_widths = c(1,1))
#dev.off()

#png(filename = "three-parameters.png", height = 6, width = 8.5, unit="in",res=600)
plot_grid(water.gap,  water.Re, water.angle, air.gap, air.Re,  air.angle,
          nrow = 2)
#dev.off()
```


## 2. Outer hairs shield inner hairs from capturing odor in air (but not water)

```{r echo=FALSE, message=FALSE, warning=FALSE}
alldatarowair.melted<-melt(alldatarow.air,id.vars = c("angle","gap","Re","array"))
alldatarowwater.melted<-melt(alldatarow.water,id.vars = c("angle","gap","Re","array"))

allrows.water<-ggplot(alldatarowwater.melted,aes(variable,value,fill=array)) + 
  #geom_violin() + 
  geom_jitter(size=1.5, color = "gray30", pch=21)+
  xlab("") + ylab("Conc captured per row")+ 
  scale_fill_viridis(discrete=TRUE)+theme_bw() + theme(legend.position = "top")
allrows.air<-ggplot(alldatarowair.melted,aes(variable,value,fill=array)) + 
  #geom_violin() + 
  geom_jitter(size=1.5, color = "gray30", pch=21)+
  xlab("") + ylab("Conc captured per row") + scale_x_discrete(position="top") +
  scale_fill_viridis(discrete=TRUE, option="C")+theme_bw() + theme(legend.position = "top")
#png(file = "jiggerrow.png", height = 3.75, width = 8.4, unit = "in", res = 500)
plot_grid(allrows.water,allrows.air)
#dev.off()
#png(filename="legend.png")
plot_grid(leg.air,leg.water)
```


Plot gap-to-diameter ratio against value: 
```{r echo=FALSE, warning=FALSE, fig.height=5.5, fig.width=4.25}
row1water <- ggplot(alldatarow.water, aes(gap, row1, fill = array)) +
  geom_point(size = 2.5, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", discrete = TRUE) + 
  xlab("Gap-to-diameter ratio") + ylab("Conc captured per row") + ylim(c(0, 200)) +
  theme_bw() + theme(legend.position = "none")
row2water <- ggplot(alldatarow.water, aes(gap, row2, fill = array)) +
  geom_point(size = 2.5, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", discrete = TRUE) + 
  xlab("Gap-to-diameter ratio") + ylab("Conc captured per row") + ylim(c(0, 200)) + 
  theme_bw() + theme(legend.position = "none")
row3water <- ggplot(alldatarow.water, aes(gap, row3, fill = array)) +
  geom_point(size = 2.5, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", discrete = TRUE) + 
  xlab("Gap-to-diameter ratio") + ylab("Conc captured per row") + ylim(c(0, 200)) + 
  theme_bw() + theme(legend.position = "none")
row4water <- ggplot(alldatarow.water, aes(gap, row4, fill = array)) +
  geom_point(size = 2.5, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", discrete = TRUE) + 
  xlab("Gap-to-diameter ratio") + ylab("Conc captured per row") + ylim(c(0, 200)) + 
  theme_bw() + theme(legend.position = "none")
row5water <- ggplot(alldatarow.water, aes(gap, row5, fill = array)) +
  geom_point(size = 4, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", discrete = TRUE) +
  theme_bw() + theme(legend.position = "bottom")
leg.water <- get_legend(row5water)
row5water <- ggplot(alldatarow.water, aes(gap, row5, fill = array)) +
  geom_point(size = 2.5, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", discrete = TRUE) + 
  xlab("Gap-to-diameter ratio") + ylab("Conc captured per row") + ylim(c(0, 200)) + 
  theme_bw() + theme(legend.position = "none")

row1air <- ggplot(alldatarow.air, aes(gap, row1, fill = array)) +
  geom_point(size = 2.5, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", option = "C", discrete = TRUE) + 
  xlab("Gap-to-diameter ratio") + ylab("Conc captured per row") + ylim(c(0, 30000)) +
  theme_bw() + theme(legend.position = "none")
row2air <- ggplot(alldatarow.air, aes(gap, row2, fill = array)) +
  geom_point(size = 2.5, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", option = "C", discrete = TRUE) + 
  xlab("Gap-to-diameter ratio") + ylab("Conc captured per row") + ylim(c(0, 30000)) + 
  theme_bw() + theme(legend.position = "none")
row3air <- ggplot(alldatarow.air, aes(gap, row3, fill = array)) +
  geom_point(size = 2.5, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", option = "C", discrete = TRUE) + 
  xlab("Gap-to-diameter ratio") + ylab("Conc captured per row") + ylim(c(0, 30000)) + 
  theme_bw() + theme(legend.position = "none")
row4air <- ggplot(alldatarow.air, aes(gap, row4, fill = array)) +
  geom_point(size = 2.5, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", option = "C", discrete = TRUE) + 
  xlab("Gap-to-diameter ratio") + ylab("Conc captured per row") + ylim(c(0, 30000)) + 
  theme_bw() + theme(legend.position = "none")
row5air <- ggplot(alldatarow.air, aes(gap, row5, fill = array)) +
  geom_point(size = 4, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", option = "C", discrete = TRUE) + 
  xlab("Gap-to-diameter ratio") + ylab("Conc captured per row") + ylim(c(0, 30000)) + 
  theme_bw() + theme(legend.position = "bottom")
leg.air <- get_legend(row5air)
row5air <- ggplot(alldatarow.air, aes(gap, row5, fill = array)) +
  geom_point(size = 2.5, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", option = "C", discrete = TRUE) + 
  xlab("Gap-to-diameter ratio") + ylab("Conc captured per row") + ylim(c(0, 30000)) + 
  theme_bw() + theme(legend.position = "none")

plot_grid(leg.water, leg.air,
          row1water, row1air, row2water, row2air, row3water, row3air, 
          row4water, row4air, row5water, row5air, 
          nrow = 6, labels=c("Water", "Air",
                             "row 1", " ",
                             "row 2", " ",
                             "row 3", " ",
                             "row 4", " ",
                             "row 5", " "), 
          label_x = c(0.45,0.45,0,0,0,0,0,0,0,0,0,0), 
          label_y = c(1.1, 1.1),
          rel_heights = c(0.75,2,2,2,2,2))
```


Plot Reynolds number against odor captured:
```{r echo=FALSE, message = FALSE, warning = FALSE, fig.height=5.5, fig.width=4.25}
#, fig.height = 10, fig.width = 8.5}

row1water <- ggplot(alldatarow.water, aes(Re, row1, fill = array)) +
  geom_point(size = 4, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", discrete = TRUE) +
  xlab("Reynolds number") + ylab("Conc captured per row") + ylim(c(0, 200)) +
  theme_bw() + theme(legend.position = "bottom")
leg.water <- get_legend(row1water)
row1water <- ggplot(alldatarow.water, aes(Re, row1, fill = array)) +
  geom_point(size = 2.5, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", discrete = TRUE) +
  xlab("Reynolds number") + ylab("Conc captured per row") + ylim(c(0, 200)) +
  theme_bw() + theme(legend.position = "none")
row2water <- ggplot(alldatarow.water, aes(Re, row2, fill = array)) +
  geom_point(size = 2.5, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", discrete = TRUE) +
  xlab("Reynolds number") + ylab("Conc captured per row") + ylim(c(0, 200)) + 
  theme_bw() + theme(legend.position = "none")
row3water <- ggplot(alldatarow.water, aes(Re, row3, fill = array)) +
  geom_point(size = 2.5, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", discrete = TRUE) +
  xlab("Reynolds number") + ylab("Conc captured per row") + ylim(c(0, 200)) + 
  theme_bw() + theme(legend.position = "none")
row4water <- ggplot(alldatarow.water, aes(Re, row4, fill = array, color=array)) +
  geom_point(size = 2.5, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", discrete = TRUE) +
  xlab("Reynolds number") + ylab("Conc captured per row") + ylim(c(0, 200)) + 
  theme_bw() + theme(legend.position = "none")
row5water <- ggplot(alldatarow.water, aes(Re, row5, fill = array)) +
  geom_point(size = 2.5, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", discrete = TRUE) +
  xlab("Reynolds number") + ylab("Conc captured per row") + ylim(c(0, 200)) + 
  theme_bw() + theme(legend.position = "none")

row1air <- ggplot(alldatarow.air, aes(Re, row1, fill = array)) +
  geom_point(size = 4, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", discrete = TRUE, option = "C") +
  xlab("Reynolds number") + ylab("Conc captured per row") + ylim(c(0, 30000)) +
  theme_bw() + theme(legend.position = "bottom")
leg.air <- get_legend(row1air)
row1air <- ggplot(alldatarow.air, aes(Re, row1, fill = array)) +
  geom_point(size = 2.5, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", discrete = TRUE, option = "C") +
  xlab("Reynolds number") + ylab("Conc captured per row") + ylim(c(0, 30000)) +
  theme_bw() + theme(legend.position = "none")
row2air <- ggplot(alldatarow.air, aes(Re, row2, fill = array, color=array)) +
  geom_point(size = 2.5, pch = 21, color = "gray30") + 
  scale_fill_viridis(discrete = TRUE, option = "C") +
  xlab("Reynolds number") + ylab("Conc captured per row") + ylim(c(0, 30000)) + 
  theme_bw() + theme(legend.position = "none")
row3air <- ggplot(alldatarow.air, aes(Re, row3, fill = array)) +
  geom_point(size = 2.5, pch = 21, color = "gray30") +
  scale_fill_viridis(name = "Array", discrete = TRUE, option = "C") +
  xlab("Reynolds number") + ylab("Conc captured per row") + ylim(c(0, 30000)) + 
  theme_bw() + theme(legend.position = "none")
row4air <- ggplot(alldatarow.air, aes(Re, row4, fill = array, color=array)) +
  geom_point(size = 2.5, pch = 21, color = "gray30") +
  scale_fill_viridis(name = "Array", discrete = TRUE, option = "C") +
  xlab("Reynolds number") + ylab("Conc captured per row") + ylim(c(0, 30000)) + 
  theme_bw() + theme(legend.position = "none")
row5air <- ggplot(alldatarow.air, aes(Re, row5, fill = array, color=array)) +
  geom_point(size = 2.5, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", discrete = TRUE, option = "C") +
  xlab("Reynolds number") + ylab("Conc captured per row") + ylim(c(0,30000)) + 
  theme_bw() + theme(legend.position = "none")

plot_grid(leg.water, leg.air,
          row1water, row1air, row2water, row2air, row3water, row3air, 
          row4water, row4air, row5water, row5air, 
          nrow = 6, labels=c("Water", "Air",
                             "row 1", " ",
                             "row 2", " ",
                             "row 3", " ",
                             "row 4", " ",
                             "row 5", " "), 
          label_x = c(0.45,0.45,0,0,0,0,0,0,0,0,0,0), 
          label_y = c(1.1, 1.1),
          rel_heights = c(0.75,2,2,2,2,2))
```


Plot angle against value: 
```{r echo=FALSE, warning=FALSE, fig.height=10,fig.width=8.5}
# fig.height=4.5, fig.width=8.5} 
#, fig.height=5.5, fig.width=4.25}
row1water <- ggplot(alldatarow.water, aes(angle, row1, fill = array)) +
  geom_point(size = 2.5, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", discrete = TRUE) + 
  xlab("Angle") + ylab("Conc captured per row") + ylim(c(0, 200)) +
  theme_bw() + theme(legend.position = "none")
row2water <- ggplot(alldatarow.water, aes(angle, row2, fill = array)) +
  geom_point(size = 2.5, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", discrete = TRUE) + 
  xlab("Angle") + ylab("Conc captured per row") + ylim(c(0, 200)) + 
  theme_bw() + theme(legend.position = "none")
row3water <- ggplot(alldatarow.water, aes(angle, row3, fill = array)) +
  geom_point(size = 2.5, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", discrete = TRUE) + 
  xlab("Angle") + ylab("Conc captured per row") + ylim(c(0, 200)) + 
  theme_bw() + theme(legend.position = "none")
row4water <- ggplot(alldatarow.water, aes(angle, row4, fill = array)) +
  geom_point(size = 2, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", discrete = TRUE) + 
  xlab("Angle") + ylab("Conc captured per row") + ylim(c(0, 200)) + 
  theme_bw() + theme(legend.position = "none")
row5water <- ggplot(alldatarow.water, aes(angle, row5, fill = array)) +
  geom_point(size = 4, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", discrete = TRUE) +
  theme_bw() + theme(legend.position = "bottom")
leg.water <- get_legend(row5water)
row5water <- ggplot(alldatarow.water, aes(angle, row5, fill = array)) +
  geom_point(size = 2.5, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", discrete = TRUE) + 
  xlab("Angle") + ylab("Conc captured per row") + ylim(c(0, 200)) + 
  theme_bw() + theme(legend.position = "none")

row1air <- ggplot(alldatarow.air, aes(angle, row1, fill = array)) +
  geom_point(size = 2.5, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", option = "C", discrete = TRUE) + 
  xlab("Angle") + ylab("Conc captured per row") + ylim(c(0, 30000)) +
  theme_bw() + theme(legend.position = "none")
row2air <- ggplot(alldatarow.air, aes(angle, row2, fill = array)) +
  geom_point(size = 2.5, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", option = "C", discrete = TRUE) + 
  xlab("Angle") + ylab("Conc captured per row") + ylim(c(0, 30000)) + 
  theme_bw() + theme(legend.position = "none")
row3air <- ggplot(alldatarow.air, aes(angle, row3, fill = array)) +
  geom_point(size = 2.5, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", option = "C", discrete = TRUE) + 
  xlab("Angle") + ylab("Conc captured per row") + ylim(c(0, 30000)) + 
  theme_bw() + theme(legend.position = "none")
row4air <- ggplot(alldatarow.air, aes(angle, row4, fill = array)) +
  geom_point(size = 2.5, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", option = "C", discrete = TRUE) + 
  xlab("Angle") + ylab("Conc captured per row") + ylim(c(0, 30000)) + 
  theme_bw() + theme(legend.position = "none")
row5air <- ggplot(alldatarow.air, aes(angle, row5, fill  = array)) +
  geom_point(size = 4, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", option = "C", discrete = TRUE) + 
  xlab("Angle") + ylab("Conc captured per row") + ylim(c(0, 30000)) + 
  theme_bw() + theme(legend.position = "bottom")
leg.air <- get_legend(row5air)
row5air <- ggplot(alldatarow.air, aes(angle, row5, fill = array)) +
  geom_point(size = 2.5, pch = 21, color = "gray30") + 
  scale_fill_viridis(name = "Array", option = "C", discrete = TRUE) + 
  xlab("Angle") + ylab("Conc captured per row") + ylim(c(0, 30000)) + 
  theme_bw() + theme(legend.position = "none")

plot_grid(leg.water, leg.air,
          row1water, row1air, row2water, row2air, row3water, row3air, 
          row4water, row4air, row5water, row5air, 
          nrow = 6,  rel_heights = c(0.75,2,2,2,2,2),
          labels=c("Water", "Air",
                             "row 1", " ",
                             "row 2", " ",
                             "row 3", " ",
                             "row 4", " ",
                             "row 5", " "), 
          label_x = c(0.45,0.45,0,0,0,0,0,0,0,0,0,0), 
          label_y = c(1.1, 1.1))
#png(filename="angle-rows.png", width=8.5, height=4.5, unit="in", res=600)
#plot_grid(row1water, row2water, row3water, row4water, row5water, leg.water,
#          row1air,  row2air, row3air, row4air, row5air, leg.air,  
#          nrow=2, rel_widths = c(1,1,1,1,1,0.65))
#dev.off()
#png(filename="angle-rows.png", width=8.5*0.5, height=9.5, unit="in", res=600)
#plot_grid(row1air,row2air,row3air,row4air,row5air,nrow = 5, rel_heights = c(1,1,1,1,1))
plot_grid(row1water,row2water,row3water,row4water,row5water,nrow = 5, rel_heights = c(1,1,1,1,1))
#dev.off()
```


### 3. Odor capture is most sensitive to changes in gap-width-to-diameter ratio for both fluids

things.


