---
title: "Dr. Waldrop's Odor-capture Notebook"
output: html_notebook
fig_width: 6
---

# Some initial plotting for the water condition

Loading data and shaping data frame:
```{r echo=TRUE, message=TRUE, warning=FALSE}
library(ggplot2) # for ggplots
library(reshape2) # for melt()
library(viridis) # for the viridis color palette
# 25-hair array
nohairs<-25
waterdata.25 <- read.csv("../results/r-csv-files/25hair_results/totalconc_water_165_2020-12-02.csv")
waterhairs25 <- subset(waterdata.25, select = c(1:3,seq(from=5,to=(4+nohairs))))
waterhairs25.melted<-melt(waterhairs25, id.vars = c("angle","gap","Re"))
# 18-hair array
nohairs <- 18
waterdata.18 <- read.csv("../results/r-csv-files/18hair_results/totalconc_water_165_2020-12-02.csv")
waterhairs18 <- subset(waterdata.18, select = c(1:3,seq(from=5,to=(4+nohairs))))
waterhairs18.melted<-melt(waterhairs18, id.vars = c("angle","gap","Re"))
```

## Hair plots

## 18-hair array
Plot Reynolds number versus odor concentration captured:
```{r echo=FALSE}
ggplot(waterhairs18.melted, aes(Re,value,color=variable)) +
  geom_point() + scale_color_viridis(name = "Hair number", discrete = TRUE, option = "A") + 
  xlab("Reynolds number") + ylab("Odor conc captured per hair") + 
  guides(color=guide_legend(ncol=2))
```
Plot gap-to-diameter ratio against value: 
```{r echo=TRUE}
ggplot(waterhairs18.melted, aes(gap, value, color = variable)) +
  geom_point() + scale_color_viridis(name = "Hair number", discrete = TRUE, option = "A") + 
  xlab("Gap-to-diameter ratio") + ylab("Odor conc captured per hair") + 
  guides(color=guide_legend(ncol=2))
```

Plot angle versus value:
```{r echo=FALSE}
ggplot(waterhairs18.melted, aes(angle, value, color = variable)) +
  geom_point() + scale_color_viridis(name = "Hair number", discrete = TRUE, option = "A") + 
  xlab("Angle of array to flow") + ylab("Odor conc captured per hair") + 
  guides(color=guide_legend(ncol=2))
```


## 25-hair array


Plot Reynolds number versus odor concentration captured:
```{r echo=FALSE}
ggplot(waterhairs25.melted, aes(Re,value,color=variable)) +
  geom_point() + scale_color_viridis(name = "Hair number", discrete = TRUE) + 
  xlab("Reynolds number") + ylab("Odor conc captured per hair") 
```

Plot gap-to-diameter ratio against value: 
```{r echo=FALSE}
ggplot(waterhairs25.melted, aes(gap,value,color=variable)) +
  geom_point() + scale_color_viridis(name = "Hair number", discrete = TRUE) + 
  xlab("Gap-to-diameter ratio") + ylab("Odor conc captured per hair") 
```


Plot angle versus value:
```{r echo=FALSE}
ggplot(waterhairs25.melted, aes(angle, value, color = variable)) +
  geom_point() + scale_color_viridis(name = "Hair number", discrete = TRUE) + 
  xlab("Angle of array to flow") + ylab("Odor conc captured per hair") 
  
```
## Individual Row Plots

Setup data frames: 
```{r}
rowdata18 <- data.frame(parameters, rep("18hair",length = length(waterdata.18$row1)), 
                        waterdata.18$row1, waterdata.18$row2, waterdata.18$row3, 
                        waterdata.18$row4, rep(NA, length = length(waterdata.18$row1)))
names(rowdata18) <- c(names(parameters),"array","row1","row2","row3","row4","row5")
rowdata25 <- data.frame(parameters, rep("25hair",length = length(waterdata.25$row1)), 
                        waterdata.25$row1, waterdata.25$row2, waterdata.25$row3, 
                        waterdata.25$row4, waterdata.25$row5)
names(rowdata25) <- c(names(parameters),"array","row1","row2","row3","row4","row5")
rowdata.water <- rbind(rowdata18,rowdata25)
rowdatawater.melted <- melt(rowdata.water, id.vars = c("angle","gap","Re","array"))
```

Plot row number versus value for both values:
```{r echo=FALSE, warning=FALSE}
ggplot(rowdatawater.melted, aes(variable, value, color = array)) +
  geom_point() + scale_color_viridis(name = "Array", discrete = TRUE) + 
  xlab("Row of array") + ylab("Odor conc captured per row") 
```

Plot gap-to-diameter ratio against value: 
```{r echo=FALSE, warning=FALSE}
ggplot(rowdatawater.melted, aes(gap,value,color=variable, shape=array)) +
  geom_point(size=2) + scale_color_viridis(name = "Row number", discrete = TRUE) + 
  xlab("Gap-to-diameter ratio") + ylab("Odor conc captured per hair") 
```
Plot gap-to-diameter ratio against value for just 18-hair array: 
```{r echo=FALSE, warning=FALSE}
subset18.rowdatawater <- rowdatawater.melted[rowdatawater.melted$array == "18hair",]
ggplot(subset18.rowdatawater, aes(gap,value,color=variable)) +
  geom_point(size=2) + scale_color_viridis(name = "Row number", discrete = TRUE) + 
  xlab("Gap-to-diameter ratio") + ylab("Odor conc captured per hair") 
```

Plot gap-to-diameter ratio against value for just 25-hair array: 
```{r echo=FALSE, warning=FALSE}
subset25.rowdatawater <- rowdatawater.melted[rowdatawater.melted$array == "25hair",]
ggplot(subset25.rowdatawater, aes(gap,value,color=variable)) +
  geom_point(size=2) + scale_color_viridis(name = "Row number", discrete = TRUE) + 
  xlab("Gap-to-diameter ratio") + ylab("Odor conc captured per hair") 
```
Plot Reynolds number against value for just 18-hair array: 
```{r echo=FALSE, warning=FALSE}
ggplot(subset18.rowdatawater, aes(Re,value,color=variable)) +
  geom_point(size=2) + scale_color_viridis(name = "Row number", discrete = TRUE) + 
  xlab("Gap-to-diameter ratio") + ylab("Odor conc captured per hair") 
```

Plot Reynolds number against value for just 25-hair array: 
```{r echo=FALSE, warning=FALSE}
ggplot(subset25.rowdatawater, aes(Re,value,color=variable)) +
  geom_point(size=2) + scale_color_viridis(name = "Row number", discrete = TRUE) + 
  xlab("Gap-to-diameter ratio") + ylab("Odor conc captured per hair") 
```

## Total Concentration Plots

Setup data frames: 
```{r echo=TRUE}
botharrays.totalconc <- data.frame(parameters, waterdata.18$total.conc, waterdata.25$total.conc)
colnames(botharrays.totalconc)<- c(colnames(parameters),"18hairs","25hairs")
botharraysconc.melted <- melt(botharrays.totalconc, id.vars = c("angle","gap","Re"))
```

Total concentration for gap-to-diameter ratio versus odor captured, arrays as colors: 
```{r echo=FALSE}
ggplot(botharraysconc.melted, aes(gap, value, color = variable)) +
  geom_point() + scale_color_viridis(discrete = TRUE)
```

Total concentration for Re versus odor captured, arrays as colors: 
```{r echo=FALSE}
ggplot(botharraysconc.melted, aes(Re, value, color = variable)) +
  geom_point() + scale_color_viridis(discrete = TRUE)
```

Total concentration for angle versus odor captured, arrays as color: 
```{r echo=FALSE}
ggplot(botharraysconc.melted, aes(angle, value, color = variable)) +
  geom_point() + scale_color_viridis(discrete = TRUE)
```

# The air condition

# 25-hair array
```{r echo=TRUE, warning=FALSE}
nohairs<-25
airdata.25 <- read.csv("../results/r-csv-files/25hair_results/totalconc_air_165_2020-12-02.csv")
waterhairs25 <- subset(waterdata.25, select = c(1:3,seq(from=5,to=(4+nohairs))))
waterhairs25.melted<-melt(waterhairs25, id.vars = c("angle","gap","Re"))
# 18-hair array
nohairs <- 18
airdata.18 <- read.csv("../results/r-csv-files/18hair_results/totalconc_air_165_2020-12-02.csv")
airhairs18 <- subset(airdata.18, select = c(1:3,seq(from=5,to=(4+nohairs))))
airhairs18.melted<-melt(airhairs18, id.vars = c("angle","gap","Re"))
```
## Hair plots

## 18-hair array

Plot Reynolds number versus odor concentration captured:
```{r echo=FALSE}
ggplot(airhairs18.melted, aes(Re,value,color=variable)) +
  geom_point() + scale_color_viridis(name = "Hair number", discrete = TRUE, option = "A") + 
  xlab("Reynolds number") + ylab("Odor conc captured per hair") + 
  guides(color=guide_legend(ncol=2))
```

Plot gap width versus odor concentration captured:
```{r echo=FALSE}
ggplot(airhairs18.melted, aes(gap,value,color=variable)) +
  geom_point() + scale_color_viridis(name = "Hair number", discrete = TRUE, option = "A") + 
  xlab("Gap-width-to-diameter Ratio") + ylab("Odor conc captured per hair") + 
  guides(color=guide_legend(ncol=2))
```


Plot angle versus odor concentration captured:
```{r echo=FALSE}
ggplot(airhairs18.melted, aes(angle,value,color=variable)) +
  geom_point() + scale_color_viridis(name = "Hair number", discrete = TRUE, option = "A") + 
  xlab("Angle") + ylab("Odor conc captured per hair") + 
  guides(color=guide_legend(ncol=2))
```

```{r echo=FALSE}
airdata18.melted <- melt(airdata.18,  id.vars = c("angle","gap","Re"))
airtotconc.18 <- airdata18.melted[airdata18.melted$variable=="total.conc",]
ggplot(airtotconc.18, aes(Re, value)) +
  geom_point() + scale_color_viridis(name = "Hair number", discrete = TRUE, option = "A") + 
  xlab("Re") + ylab("Total Odor conc captured ") + 
  guides(color=guide_legend(ncol=2))
```

```{r echo=FALSE}
ggplot(airtotconc.18, aes(gap, value)) +
  geom_point() + scale_color_viridis(name = "Hair number", discrete = TRUE, option = "A") + 
  xlab("Gap-width-to-diameter ratio") + ylab("Odor conc captured per hair") + 
  guides(color=guide_legend(ncol=2))
```

```{r echo=FALSE}
ggplot(airtotconc.18, aes(angle, value)) +
  geom_point() + scale_color_viridis(name = "Hair number", discrete = TRUE, option = "A") + 
  xlab("Angle") + ylab("Odor conc captured per hair") + 
  guides(color=guide_legend(ncol=2))
```