---
title: "Dr. Waldrop's Fluid-flow Notebook"
output: html_notebook
fig_width: 6
---

# Some initial plotting of fluid flow

Initial package loading and function definitions: 
```{r echo=TRUE, warning=TRUE, message=TRUE}
library(ggplot2) # for ggplots
library(reshape2) # for melt()
library(viridis) # for the viridis color palette

# Sourcing data handling functions
source("../src/r-scripts/datahandling_functions.R")

n <- 165 # Number of simulations in set

# Loading individual data sets
fluxdata_3 <- loadnshapedata(n,"flux",3,"2020-12-06")
fluxdata_18 <- loadnshapedata(n,"flux",18,"2020-12-02")
fluxdata_25 <- loadnshapedata(n,"flux",25,"2020-12-02")
sheardata_3 <- loadnshapedata(n,"shearhairs",3,"2020-12-04")
sheardata_18 <- loadnshapedata(n,"shearhairs",18,"2020-12-04")
sheardata_25 <- loadnshapedata(n,"shearhairs",25,"2020-12-06")
leakinessdata_3 <- loadnshapedata(n,"leakiness",3,"2020-12-06")
leakinessdata_18 <- loadnshapedata(n,"leakiness",18,"2020-12-02")
leakinessdata_25 <- loadnshapedata(n,"leakiness",25,"2020-12-02")
Umeandata_3 <- loadnshapedata(n,"Umean",3,"2020-12-06")
Umeandata_18 <- loadnshapedata(n,"Umean",18,"2020-12-02")
Umeandata_25 <- loadnshapedata(n,"Umean",25,"2020-12-02")

# Stitching sets together
allflux <- stitchdata(n,"flux",fluxdata_18,fluxdata_25,18,25)
allshear <- stitchdata(n,"shear",sheardata_18,sheardata_25,18,25)
allleak <- stitchdata(n,"leakiness",leakinessdata_18,leakinessdata_25,18,25)
allUmean <- stitchdata(n,"Umean",Umeandata_18,Umeandata_25,18,25)

# Melting sets
allflux.melted <- melt(allflux, id.vars = c("angle","gap","Re","array"))
allshear.melted <- melt(allshear, id.vars = c("angle","gap","Re","array"))
allleak.melted <- melt(allleak, id.vars = c("angle","gap","Re","array"))
allUmean.melted <- melt(allUmean, id.vars = c("angle","gap","Re","array"))
```

## Flux 

Plot flux for each hair and both arrays: 
```{r echo=FALSE, warning=FALSE}
ggplot(allflux.melted, aes(variable, value, color = array)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, option = "C") + 
  xlab(" ") + ylab("Flux") +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))
```
### 3-hair array
Plot Flux against Reynolds number: 
```{r echo=FALSE, warning=FALSE}
fluxdata_3.melted<-melt(fluxdata_3, id.vars = c("angle","gap","Re","array"))
ggplot(fluxdata_3.melted, aes(Re, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Re") + ylab("Flux")
```

```{r echo=FALSE, warning=FALSE}
ggplot(fluxdata_3.melted, aes(gap, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Gap-to-diameter ratio") + ylab("Flux")
```

```{r echo=FALSE, warning=FALSE}
ggplot(fluxdata_3.melted, aes(angle, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Angle") + ylab("Flux")
```

### 18-hair array

Plot Flux against Reynolds number: 
```{r echo=FALSE, warning=FALSE}
subset18.datawater <- allflux.melted[allflux.melted$array=="18hair",]
ggplot(subset18.datawater, aes(Re, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Re") + ylab("Flux")
```
Plot Flux against gap width: 
```{r echo=FALSE, warning=FALSE}
ggplot(subset18.datawater, aes(gap, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Gap-width-to-diameter Ratio") + ylab("Flux")
```
Plot flux against angle:
```{r echo=FALSE, warning=FALSE}
ggplot(subset18.datawater, aes(angle, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Angle") + ylab("Flux")
```

### 25-hair array

Plot Flux against Reynolds number: 
```{r echo=FALSE, warning=FALSE}
subset25.datawater <- allflux.melted[allflux.melted$array=="25hair",]
ggplot(subset25.datawater, aes(Re, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Re") + ylab("Flux")
```
Plot Flux against gap width: 
```{r echo=FALSE, warning=FALSE}
ggplot(subset25.datawater, aes(gap, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Gap-width-to-diameter Ratio") + ylab("Flux")
```
Plot flux against angle:
```{r echo=FALSE, warning=FALSE}
ggplot(subset25.datawater, aes(angle, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Angle") + ylab("Flux")
```

## Shear


Plot shear for each hair and both arrays: 
```{r echo=FALSE, warning=FALSE}
ggplot(allshear.melted, aes(variable, value, color = array)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, option = "C") + 
  xlab(" ") + ylab("Shear") +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))
```

### 3-hair array

```{r echo=FALSE, warning=FALSE}
sheardata_3.melted<-melt(sheardata_3, id.vars = c("angle","gap","Re","array"))
ggplot(sheardata_3.melted, aes(Re, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Re") + ylab("Shear")
```

```{r echo=FALSE, warning=FALSE}
ggplot(sheardata_3.melted, aes(gap, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Gap-to-diameter ratio") + ylab("Shear")
```

```{r echo=FALSE, warning=FALSE}
ggplot(sheardata_3.melted, aes(angle, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Angle") + ylab("Shear")
```


### 18-hair array

Plot shear against Reynolds number: 
```{r echo=FALSE, warning=FALSE}
rm(subset18.datawater)
subset18.datawater <- allshear.melted[allshear.melted$array=="18hair",]
ggplot(subset18.datawater, aes(Re, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Re") + ylab("Shear")
```
Plot shear against gap width: 
```{r echo=FALSE, warning=FALSE}
ggplot(subset18.datawater, aes(gap, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Gap-width-to-diameter Ratio") + ylab("Shear")
```
Plot shear against angle:
```{r echo=FALSE, warning=FALSE}
ggplot(subset18.datawater, aes(angle, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Angle") + ylab("Shear")
```

### 25-hair array

Plot shear against Reynolds number: 
```{r echo=FALSE, warning=FALSE}
rm(subset25.datawater)
subset25.datawater <- allshear.melted[allshear.melted$array=="25hair",]
ggplot(subset25.datawater, aes(Re, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Re") + ylab("Shear")
```
Plot shear against gap width: 
```{r echo=FALSE, warning=FALSE}
ggplot(subset25.datawater, aes(gap, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Gap-width-to-diameter Ratio") + ylab("Shear")
```
Plot shear against angle:
```{r echo=FALSE, warning=FALSE}
ggplot(subset25.datawater, aes(angle, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Angle") + ylab("Shear")
```

## Umean

Plot $U_{mean}$ for each hair and both arrays: 
```{r echo=FALSE, warning=FALSE}
ggplot(allUmean.melted, aes(variable, value, color = array)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, option = "C") + 
  xlab(" ") + ylab("Umean") +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))
```
### 3-hair array

```{r echo=FALSE, warning=FALSE}
Umeandata_3.melted<-melt(Umeandata_3, id.vars = c("angle","gap","Re","array"))
ggplot(Umeandata_3.melted, aes(Re, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Re") + ylab("Umean")
```

```{r echo=FALSE, warning=FALSE}
ggplot(Umeandata_3.melted, aes(gap, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Gap-to-diameter ratio") + ylab("Umean")
```

```{r echo=FALSE, warning=FALSE}
ggplot(Umeandata_3.melted, aes(angle, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Angle") + ylab("Umean")
```
### 18-hair array

Plot $U_{mean}$ against Reynolds number: 
```{r echo=FALSE, warning=FALSE}
rm(subset18.datawater)
subset18.datawater <- allUmean.melted[allUmean.melted$array=="18hair",]
ggplot(subset18.datawater, aes(Re, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Re") + ylab("Umean")
```
Plot $U_{mean}$ against gap width: 
```{r echo=FALSE, warning=FALSE}
ggplot(subset18.datawater, aes(gap, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Gap-width-to-diameter Ratio") + ylab("Umean")
```
Plot $U_{mean}$ against angle:
```{r echo=FALSE, warning=FALSE}
ggplot(subset18.datawater, aes(angle, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Angle") + ylab("Umean")
```

### 25-hair array

Plot $U_{mean}$ against Reynolds number: 
```{r echo=FALSE, warning=FALSE}
rm(subset25.datawater)
subset25.datawater <- allUmean.melted[allUmean.melted$array=="25hair",]
ggplot(subset25.datawater, aes(Re, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Re") + ylab("Umean")
```
Plot $U_{mean}$ against gap width: 
```{r echo=FALSE, warning=FALSE}
ggplot(subset25.datawater, aes(gap, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Gap-width-to-diameter Ratio") + ylab("Umean")
```
Plot $U_{mean}$ against angle:
```{r echo=FALSE, warning=FALSE}
ggplot(subset25.datawater, aes(angle, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Angle") + ylab("Umean")
```

## Leakiness

Plot leakiness for each row and both arrays: 
```{r echo=FALSE, warning=FALSE}
ggplot(allleak.melted, aes(variable, value, color = array)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, option = "C") + 
  xlab(" ") + ylab("Leakiness") +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))
```

```{r echo=FALSE, warning=FALSE}
ggplot(allleak.melted, aes(variable, value, color = array)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, option = "C") + 
  xlab(" ") + ylab("Leakiness") +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))
```

### 3-hair array

```{r echo=FALSE, warning=FALSE}
leakdata_3.melted<-melt(leakinessdata_3, id.vars = c("angle","gap","Re","array"))
ggplot(leakdata_3.melted, aes(Re, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Re") + ylab("Leakiness")
```

```{r echo=FALSE, warning=FALSE}
ggplot(leakdata_3.melted, aes(gap, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Gap-to-diameter ratio") + ylab("Leakiness")
```

```{r echo=FALSE, warning=FALSE}
ggplot(leakdata_3.melted, aes(angle, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Angle") + ylab("Leakiness")
```

### 18-hair array

Plot leakiness against Reynolds number: 
```{r echo=FALSE, warning=FALSE}
rm(subset18.datawater)
subset18.datawater <- allleak.melted[allleak.melted$array=="18hair",]
ggplot(subset18.datawater, aes(Re, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Row number", option = "A") + 
  xlab("Re") + ylab("Leakness")
```
Plot leakiness against gap width: 
```{r echo=FALSE, warning=FALSE}
ggplot(subset18.datawater, aes(gap, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Row number", option = "A") + 
  xlab("Gap-width-to-diameter Ratio") + ylab("Leakiness")
```
Plot leakiness against angle:
```{r echo=FALSE, warning=FALSE}
ggplot(subset18.datawater, aes(angle, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Row number", option = "A") + 
  xlab("Angle") + ylab("Leakiness")
```

### 25-hair array

Plot leakiness against Reynolds number: 
```{r echo=FALSE, warning=FALSE}
rm(subset25.datawater)
subset25.datawater <- allleak.melted[allleak.melted$array=="25hair",]
ggplot(subset25.datawater, aes(Re, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Row number", option = "A") + 
  xlab("Re") + ylab("Leakiness")
```
Plot leakiness against gap width: 
```{r echo=FALSE, warning=FALSE}
ggplot(subset25.datawater, aes(gap, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Row number", option = "A") + 
  xlab("Gap-width-to-diameter Ratio") + ylab("Leakiness")
```
Plot leakiness against angle:
```{r echo=FALSE, warning=FALSE}
ggplot(subset25.datawater, aes(angle, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Row number", option = "A") + 
  xlab("Angle") + ylab("Leakiness")
```

Plot leakiness against Re:
```{r echo=FALSE, warning=FALSE}
subset25.datawater<-
ggplot(subset25.datawater, aes(angle, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Row number", option = "A") + 
  xlab("Angle") + ylab("Leakiness")
```