---
title: "Dr. Waldrop's Fluid-flow Notebook"
output:
  pdf_document: default
  html_notebook: default
fig_width: 6
---



## Intro


```{r setup}

library(tidyr)
library(ggplot2) # for ggplots
library(patchwork)
library(viridis) # for the viridis color palette

# Sourcing data handling functions
source("./src/r-scripts/datahandling_functions.R")
```


The entcode master project is a computational fluid dynamic simulation of odor capture by a chemosensory hair array consisting of three hairs and a supporting, non-chemosensory antenna. The simulations are in two dimensions, representing a cross-section of the array, and represent arrays with either 3 or 25 hairs. The project consists of setup for 2,000 individual simulations, each representing a unique combination of the following parameters: 

 * angle: Angle of array to oncoming flow: 0 to 180 degrees
 * gap: Gap-to-hair-diameter ratio of the gaps between chemosensory hairs to their widths: 1 to 50
 * ant: Antenna-to-hair-diameter ratio of the diameter of a chemosensory hair to the diameter of the supporting antenna: 1 to 50
 * dist: Distance of the center hair from the antenna: 0.001 to 0.02 m
 * re: Reynolds number: 0.1 to 10
 * diff_coef: Odor diffusion coefficient: 1e-9 to 1e-4 m$^2$ s$^{-1}$
 * stink_width: Width of the initial odor stripe: 0.5 to 5 % of the domain width
 * init_conc: Initial odor concentration: 1e3 to 1e7 (no units)


```{r include=FALSE}
three_hair <- read.csv("./results/r-csv-files/3hair_results/flowdata_2022-11-11.csv")
twofive_hair <- read.csv("./results/r-csv-files/25hair_results/flowdata_2023-06-28.csv", row.names=1)

plot_parameter <- function(three_dat, twofive_dat, parameter, output){
  # 3 hair
  p3 <- ggplot(three_dat, aes_string(parameter, output)) + geom_point() +
    ggtitle("3 hair") + theme_minimal()
  # 25 hair
  p25 <- ggplot(twofive_dat, aes_string(parameter, output)) + geom_point() + 
    ggtitle("25 hair") + theme_minimal()
  return(p3 + p25)
}

plot_values <- function(dat, output, variable){
  col_list <- grep(output, colnames(dat))
  col_list <- c(1:6, col_list)
  dat_sub <- dat[,col_list]
  dat_longer <- pivot_longer(dat_sub, cols = !c(1:6), names_prefix = paste0(output,"_"))
  dat_longer$name <- factor(dat_longer$name)
  num <- nlevels(dat_longer$name)
  dat_longer$name <- factor(dat_longer$name, ordered = T, levels = seq(1,num))
  p1<- ggplot(dat_longer, aes_string(variable, "value", fill = "name",  color = "name")) + 
    geom_point(pch = 21) +
    scale_fill_viridis(discrete = T) + 
    scale_color_viridis(discrete = T) +
    ylab(output) + theme_minimal()
  return(p1)
}

```

## Single parameter plots

Rows are labeled as 1 for the three hair array and 1 (closest to antennule) to 5 (furthest from antennule).

Plot leakiness row 1 for both arrays against angle: 

```{r echo=FALSE, warning=FALSE}
plot_parameter(three_hair, twofive_hair, "angle", "leakiness_row_1")
```

Plot leakiness row 1 for both arrays against Re: 

```{r echo=FALSE, warning=FALSE}
plot_parameter(three_hair, twofive_hair, "re", "leakiness_row_1")
```
Plot leakiness row 1 for both arrays against distance from antenna: 

```{r echo=FALSE, warning=FALSE}
plot_parameter(three_hair, twofive_hair, "dist", "leakiness_row_1")
```

Plot leakiness row 1 for both arrays against antenna width: 

```{r echo=FALSE, warning=FALSE}
plot_parameter(three_hair, twofive_hair, "ant", "leakiness_row_1")
```

Plot leakiness row 1 for both arrays against gap width: 

```{r echo=FALSE, warning=FALSE}
plot_parameter(three_hair, twofive_hair, "gap", "leakiness_row_1")
```

## Plots with individual hairs

Individual hairs are numbered 1 through 3 for the 3-hair array and 1 through 25 for the 25-hair array. The higher the number indicates the further away the hair is from the antennule base. 

Shear across hairs: 

```{r message=FALSE, warning=FALSE}
(plot_values(three_hair, "shear_hair", "re") + plot_values(twofive_hair, "shear_hair", "re") )/
  (plot_values(three_hair, "shear_hair", "angle") + plot_values(twofive_hair, "shear_hair", "angle") ) /
  (plot_values(three_hair, "shear_hair", "gap") + plot_values(twofive_hair, "shear_hair", "gap") ) + 
  plot_layout(guides = "collect")
```


U mean around hairs: 

```{r}
(plot_values(three_hair, "Umean_hair", "re") + plot_values(twofive_hair, "Umean_hair", "re") )/
  (plot_values(three_hair, "Umean_hair", "angle") + plot_values(twofive_hair, "Umean_hair", "angle") ) /
  (plot_values(three_hair, "Umean_hair", "gap") + plot_values(twofive_hair, "Umean_hair", "gap") ) + 
  plot_layout(guides = "collect")
```

Flux around hairs: 
```{r}
(plot_values(three_hair, "flux_hair", "re") + plot_values(twofive_hair, "flux_hair", "re") )/
  (plot_values(three_hair, "flux_hair", "angle") + plot_values(twofive_hair, "flux_hair", "angle") ) /
  (plot_values(three_hair, "flux_hair", "gap") + plot_values(twofive_hair, "flux_hair", "gap") ) + 
  plot_layout(guides = "collect")
```

Leakiness: 

```{r}
(plot_values(three_hair, "leakiness_row", "re") + plot_values(twofive_hair, "leakiness_row", "re") )/
  (plot_values(three_hair, "leakiness_row", "angle") + plot_values(twofive_hair, "leakiness_row", "angle") ) /
  (plot_values(three_hair, "leakiness_row", "ant") + plot_values(twofive_hair, "leakiness_row", "ant") ) /
  (plot_values(three_hair, "leakiness_row", "dist") + plot_values(twofive_hair, "leakiness_row", "dist") ) /
  (plot_values(three_hair, "leakiness_row", "gap") + plot_values(twofive_hair, "leakiness_row", "gap") ) + 
  plot_layout(guides = "collect")
```