---
title: "Dr. Waldrop's Fluid-flow Notebook"
output: html_notebook
fig_width: 6
---

# Some initial plotting of fluid flow

Initial package loading and function definitions: 
```{r echo=TRUE, warning=FALSE, message=FALSE}
library(ggplot2) # for ggplots
library(reshape2) # for melt()
library(viridis) # for the viridis color palette

n <- 165

#source("../src/r-scripts/datahandling_functions.R")

findnorows <- function(nohairs){
  norows <- switch(as.character(nohairs),
                     "3" = 1,
                     "5" = 1,
                     "7" = 2,
                     "12" = 3,
                     "18" = 4,
                     "25" = 5)
  return(norows)
}

reordercols<- function(data,nohairs,datatype){
  parameter.names<-colnames(data[1:3])
  if(datatype=="leakiness"){
    norows<-findnorows(nohairs)
    rownames <- as.character(rep(0, norows))
    for (i in 1:norows) rownames[i] <- paste("row", i, sep = "") 
    new.order <- c(parameter.names, "array", rownames)
  }else {
    hairnames <- as.character(rep(0, nohairs)) # Allocates space for names 
    for (i in 1:nohairs) hairnames[i] <- paste("hair", i, sep = "") 
    new.order <- c(parameter.names,"array",hairnames)
  }
  newdata <- data[,new.order]
  return(newdata)
}

loadnshapedata<-function(n,datatype,nohairs,date) {
  data <- read.csv(paste("../results/r-csv-files/",nohairs,"hair_results/", datatype, "_", n, "_", date, ".csv", sep = ""))
  columns <- colnames(data)
  data2 <- data.frame(data, rep(paste(nohairs, "hair", sep = ""), length = n))
  colnames(data2) <- c(columns, "array")
  data.final <- reordercols(data2,nohairs,datatype)
  return(data.final)
}

stitchdata <- function(n,datatype,data1,data2,nohairs1,nohairs2){
  if(datatype=="leakiness"){
    norows1<-findnorows(nohairs1)
    norows2<-findnorows(nohairs2)
    deltah <- norows2 - norows1
    repnames <- colnames(data1)
    for (i in 1:deltah) {
      data1 <- cbind(data1, rep(NA,length=n))
      repnames <- c(repnames,paste("row",(norows1+i),sep=""))
    }
    colnames(data1)<-repnames
  } else {
    deltah <- nohairs2 - nohairs1
    repnames <- colnames(data1)
    for (i in 1:deltah) {
      data1 <- cbind(data1, rep(NA,length=n))
      repnames <- c(repnames,paste("hair",(nohairs1+i),sep=""))
    }
    colnames(data1)<-repnames
  }
  alldata <- rbind(data1,data2)
  return(alldata)
}

fluxdata_18 <- loadnshapedata(n,"flux",18,"2020-12-02")
fluxdata_25 <- loadnshapedata(n,"flux",25,"2020-12-02")
sheardata_18 <- loadnshapedata(n,"shearhairs",18,"2020-12-04")
sheardata_25 <- loadnshapedata(n,"shearhairs",25,"2020-12-02")
leakinessdata_18 <- loadnshapedata(n,"leakiness",18,"2020-12-02")
leakinessdata_25 <- loadnshapedata(n,"leakiness",25,"2020-12-02")
Umeandata_18 <- loadnshapedata(n,"Umean",18,"2020-12-02")
Umeandata_25 <- loadnshapedata(n,"Umean",25,"2020-12-02")

allflux <- stitchdata(n,"flux",fluxdata_18,fluxdata_25,18,25)
allshear <- stitchdata(n,"shear",sheardata_18,sheardata_25,18,25)
allleak <- stitchdata(n,"leakiness",leakinessdata_18,leakinessdata_25,18,25)
allUmean <- stitchdata(n,"Umean",Umeandata_18,Umeandata_25,18,25)

allflux.melted <- melt(allflux, id.vars = c("angle","gap","Re","array"))
allshear.melted <- melt(allshear, id.vars = c("angle","gap","Re","array"))
allleak.melted <- melt(allleak, id.vars = c("angle","gap","Re","array"))
allUmean.melted <- melt(allUmean, id.vars = c("angle","gap","Re","array"))
```

## Flux 

Plot flux for each hair and both arrays: 
```{r echo=FALSE, warning=FALSE}
ggplot(allflux.melted, aes(variable, value, color = array)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, option = "C") + 
  xlab(" ") + ylab("Flux") +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))
```

### 18-hair array

Plot Flux against Reynolds number: 
```{r echo=FALSE, warning=FALSE}
subset18.datawater <- allflux.melted[allflux.melted$array=="18hair",]
ggplot(subset18.datawater, aes(Re, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Re") + ylab("Flux")
```
Plot Flux against gap width: 
```{r echo=FALSE, warning=FALSE}
ggplot(subset18.datawater, aes(gap, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Gap-width-to-diameter Ratio") + ylab("Flux")
```
Plot flux against angle:
```{r echo=FALSE, warning=FALSE}
ggplot(subset18.datawater, aes(angle, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Angle") + ylab("Flux")
```

### 25-hair array

Plot Flux against Reynolds number: 
```{r echo=FALSE, warning=FALSE}
subset25.datawater <- allflux.melted[allflux.melted$array=="25hair",]
ggplot(subset25.datawater, aes(Re, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Re") + ylab("Flux")
```
Plot Flux against gap width: 
```{r echo=FALSE, warning=FALSE}
ggplot(subset25.datawater, aes(gap, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Gap-width-to-diameter Ratio") + ylab("Flux")
```
Plot flux against angle:
```{r echo=FALSE, warning=FALSE}
ggplot(subset25.datawater, aes(angle, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Angle") + ylab("Flux")
```

## Shear


Plot shear for each hair and both arrays: 
```{r echo=FALSE, warning=FALSE}
ggplot(allshear.melted, aes(variable, value, color = array)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, option = "C") + 
  xlab(" ") + ylab("Shear") +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))
```

### 18-hair array

Plot shear against Reynolds number: 
```{r echo=FALSE, warning=FALSE}
rm(subset18.datawater)
subset18.datawater <- allshear.melted[allshear.melted$array=="18hair",]
ggplot(subset18.datawater, aes(Re, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Re") + ylab("Shear")
```
Plot shear against gap width: 
```{r echo=FALSE, warning=FALSE}
ggplot(subset18.datawater, aes(gap, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Gap-width-to-diameter Ratio") + ylab("Shear")
```
Plot shear against angle:
```{r echo=FALSE, warning=FALSE}
ggplot(subset18.datawater, aes(angle, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Angle") + ylab("Shear")
```

### 25-hair array

Plot shear against Reynolds number: 
```{r echo=FALSE, warning=FALSE}
rm(subset25.datawater)
subset25.datawater <- allshear.melted[allshear.melted$array=="25hair",]
ggplot(subset25.datawater, aes(Re, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Re") + ylab("Shear")
```
Plot shear against gap width: 
```{r echo=FALSE, warning=FALSE}
ggplot(subset25.datawater, aes(gap, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Gap-width-to-diameter Ratio") + ylab("Shear")
```
Plot shear against angle:
```{r echo=FALSE, warning=FALSE}
ggplot(subset25.datawater, aes(angle, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Angle") + ylab("Shear")
```

## Umean

Plot $U_{mean}$ for each hair and both arrays: 
```{r echo=FALSE, warning=FALSE}
ggplot(allUmean.melted, aes(variable, value, color = array)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, option = "C") + 
  xlab(" ") + ylab("Umean") +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))
```

### 18-hair array

Plot $U_{mean}$ against Reynolds number: 
```{r echo=FALSE, warning=FALSE}
rm(subset18.datawater)
subset18.datawater <- allUmean.melted[allUmean.melted$array=="18hair",]
ggplot(subset18.datawater, aes(Re, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Re") + ylab("Umean")
```
Plot $U_{mean}$ against gap width: 
```{r echo=FALSE, warning=FALSE}
ggplot(subset18.datawater, aes(gap, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Gap-width-to-diameter Ratio") + ylab("Umean")
```
Plot $U_{mean}$ against angle:
```{r echo=FALSE, warning=FALSE}
ggplot(subset18.datawater, aes(angle, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Angle") + ylab("Umean")
```

### 25-hair array

Plot $U_{mean}$ against Reynolds number: 
```{r echo=FALSE, warning=FALSE}
rm(subset25.datawater)
subset25.datawater <- allUmean.melted[allUmean.melted$array=="25hair",]
ggplot(subset25.datawater, aes(Re, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Re") + ylab("Umean")
```
Plot $U_{mean}$ against gap width: 
```{r echo=FALSE, warning=FALSE}
ggplot(subset25.datawater, aes(gap, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Gap-width-to-diameter Ratio") + ylab("Umean")
```
Plot $U_{mean}$ against angle:
```{r echo=FALSE, warning=FALSE}
ggplot(subset25.datawater, aes(angle, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Hair number", option = "A") + 
  xlab("Angle") + ylab("Umean")
```

## Leakiness

Plot leakiness for each row and both arrays: 
```{r echo=FALSE, warning=FALSE}
ggplot(allleak.melted, aes(variable, value, color = array)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, option = "C") + 
  xlab(" ") + ylab("Leakiness") +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))
```

```{r echo=FALSE}
ggplot(allleak.melted, aes(variable, value, color = array)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, option = "C") + 
  xlab(" ") + ylab("Leakiness") +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))
```

### 18-hair array

Plot leakiness against Reynolds number: 
```{r echo=FALSE, warning=FALSE}
rm(subset18.datawater)
subset18.datawater <- allleak.melted[allleak.melted$array=="18hair",]
ggplot(subset18.datawater, aes(Re, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Row number", option = "A") + 
  xlab("Re") + ylab("Leakness")
```
Plot leakiness against gap width: 
```{r echo=FALSE, warning=FALSE}
ggplot(subset18.datawater, aes(gap, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Row number", option = "A") + 
  xlab("Gap-width-to-diameter Ratio") + ylab("Leakiness")
```
Plot leakiness against angle:
```{r echo=FALSE, warning=FALSE}
ggplot(subset18.datawater, aes(angle, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Row number", option = "A") + 
  xlab("Angle") + ylab("Leakiness")
```

### 25-hair array

Plot leakiness against Reynolds number: 
```{r echo=FALSE, warning=FALSE}
rm(subset25.datawater)
subset25.datawater <- allleak.melted[allleak.melted$array=="25hair",]
ggplot(subset25.datawater, aes(Re, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Row number", option = "A") + 
  xlab("Re") + ylab("Leakiness")
```
Plot leakiness against gap width: 
```{r echo=FALSE, warning=FALSE}
ggplot(subset25.datawater, aes(gap, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Row number", option = "A") + 
  xlab("Gap-width-to-diameter Ratio") + ylab("Leakiness")
```
Plot leakiness against angle:
```{r echo=FALSE, warning=FALSE}
ggplot(subset25.datawater, aes(angle, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Row number", option = "A") + 
  xlab("Angle") + ylab("Leakiness")
```

Plot leakiness against Re:
```{r echo=FALSE, warning=FALSE}
subset25.datawater<-
ggplot(subset25.datawater, aes(angle, value, color = variable)) + 
  geom_point() + scale_color_viridis(discrete = TRUE, name = "Row number", option = "A") + 
  xlab("Angle") + ylab("Leakiness")
```